\documentclass[fontsize=10pt]{tccv}
\usepackage[english]{babel}
\usepackage{fancyvrb}

\begin{document}
	
	\part{Rakin Uddin}
	
	\section{Experience}
	
	\begin{eventlist}
		
		\item{May 2017 -- Aug 2017}
		{Ontario Ministry of Education, Toronto}
		{Software Developer (Full Stack)}
		
		$\bullet$ Took ownership of 2 data-driven applications, delivering new features using XML, JSON, HTML/CSS, AngularJS, C\# and SQL to be used by 150+ board users across Ontario.\newline
		$\bullet$ Collaborated with PMs and QAs to resolve defects across 5+ applications and framework.\newline
		$\bullet$ Developed many asynchronous backend services in C\# and LINQ which reduced application loading time by 3x.\newline
		$\bullet$ Introduced a modular, scalable XLSX parsing library in C\# enabling developers to implement customized Excel file upload jobs for their applications.
		
		\item{Sept 2017 -- Present}
		{University of Toronto Scarborough, Toronto}
		{Undergraduate Teaching Assistant}
		
		$\bullet$ Managed classroom sessions of 30+ students.\newline
		$\bullet$ Reviewed relevant course concepts along with examples to further deepen student’s understanding of material.\newline
		$\bullet$ Graded assessed work ranging from quizzes to midterms and exams.
		
		\item{Sept 2016 -- Apr 2017}
		{Ontario Ministry of Education, Toronto}
		{Cloud Infrastructure Developer}
		
		$\bullet$ Engineered and implemented secure, scalable, multi-tier cloud infrastructure with another teammate using the Microsoft Azure IaaS platform.\newline
		$\bullet$ Developed automated scripts in Batch files and Windows PowerShell, one reduced operational costs by 52\% in 4+ Proof-of-Concept systems.\newline
		$\bullet$ Integrated Infrastructure as Code (IaC) processes by capturing state/configuration of PoC systems into JSON templates, enabling one-touch deployment of infrastructure.
		
		\item{Sept 2016 -- Dec 2016}
		{Ontario Ministry of Education, Toronto}
		{Application Support Analyst}
		
		$\bullet$ Developed automated test cases using Oracle SQL Developer/PL-SQL, applying reusable and scalable design principles.\newline
		$\bullet$ Performed automated regression and UAT testing with HP Quality Centre and HP QuickTest Pro for upcoming software releases.\newline
		$\bullet$ Collaborated with a team of 12 members to perform manual UAT testing on new features in 3+ large application stacks before approaching deadlines.
		
	\end{eventlist}
	
	\personal
	{\href{linkedin.com/in/rakinuddin}{linkedin.com/in/rakinuddin}}
	{(647) 678-9569}
	{rakin.uddin@mail.utoronto.ca}
	
	\section{Education}
	
	\begin{yearlist}
		
		\item{Sept 2015 -- Apr 2019}
		{Computer Science\newline Software Engineering Specialist}
		{University of Toronto Scarborough, Toronto}
		
	\end{yearlist}
	
	\section{Projects}
	
	\begin{yearlist}
		
		\item{2017}
		{\href{https://github.com/ItsMeWithTheFace/PaperFace}{PaperFace}}
		{Paper-themed watchface for Pebble Time}
		
		\item{2017}
		{\href{https://github.com/ItsMeWithTheFace/DE2Keyboard}{DE2Keyboard}}
		{A musical keyboard for the Altera DE2}
		
		\item{2017}
		{Vote Predictor}
		{Machine learning vote prediction app made with MongoDB, Node.js and Azure}
		
		\item{2016}
		{\href{https://github.com/ItsMeWithTheFace/NewNews}{NewNews}}
		{News aggregation web app made with MEAN Stack}
		
		\item{2016}
		{\href{https://github.com/ItsMeWithTheFace/JShell}{JShell}}
		{Mock UNIX shell program based in Java}
		
	\end{yearlist}
	
	\section{Skills}
	
	\begin{factlist}
		
		\item{Languages}
		{Java, Python, C\#, C, MEAN, JSON/XML, HTML/CSS, AngularJS, UNIX/Linux/PowerShell/DOS, SQL, Scheme, Haskell, Verilog, Assembly}
		
		\item{Databases}
		{MongoDB, Oracle, MySQL}
		
		\item{Cloud Frameworks}
		{Microsoft Azure, IBM Softlayer}
		
		\item {Testing}
		{PyUnit, JUnit, GDB, HUnit, HP QuickTest Professional, black-box/white-box, regression, user-acceptance testing}
		
		\item{Version Control}
		{Git, Subversion, Team Foundation Server}
		
	\end{factlist}
	
\end{document}
